### 2015-03-28 markdown/manuscript.tex
scenario placeholder'

% kramdown -o latex markdown/manuscript.md > markdown/manuscript.tex

@@

\begin{itemize}
\item add one {\tt operator}
\item add one {\tt rubric}, which may create other \emph{entailed} {\tt rubrics} as described above
\end{itemize}

@@

During its turn, the System player adds a specified minimum number of new {\tt answers} to the tableau. It follows a single rote cycle to do so:

@@

\subsubsection{Interface, the \emph{Goal} of the Exercise}\hypertarget{interface-the-goal-of-the-exercise}{}\label{interface-the-goal-of-the-exercise}

>>>>

% kramdown -o latex markdown/session.md > markdown/session.tex
% kramdown -o latex markdown/manuscript.md > markdown/manuscript.tex

@@

If we think of the tableau as a ``spreadsheet'' with a small list of {\tt operators} and a large sheet of {\tt answers} as rows and {\tt rubrics} as columns, the User can add one new {\tt operator} or one new column.

\begin{itemize}
\item add (or activate from a pre-existing list) exactly one {\tt operator}
\item add exactly one {\tt rubric}, which may in turn create other \emph{entailed} {\tt rubrics} as described above
\end{itemize}

@@

During its turn, the System player adds a specified minimum number of new {\tt answers} to the tableau. If we think of the tableau as a ``spreadsheet'' the System can only add new {\tt answers}. It follows a single rote cycle to do so:

@@

\subsubsection{Interface: the Goal of the Exercise}\hypertarget{interface-the-goal-of-the-exercise}{}\label{interface-the-goal-of-the-exercise}

### 2015-03-28 markdown/session.tex
scenario placeholder'

(test placeholder)

\begin{description}
\item[{\tt me}] I do and say a thing here

This is a continuation of the first item, and should include a few extra fillips, like $x=y$ and a little

\begin{itemize}
\item list
\item of
\item items
\end{itemize}

And also it includes a

\begin{quote}
blockquote right here
\end{quote}

@@

\item[{\tt me}] he look I can have a little dialog sortof

@@

>>>>

\textbf{Placeholder}: I am converting the transcript of the session from an awful multipage LaTeX {\tt \textbackslash{}longtable} into a much more manageable {\tt \textbackslash{}enum} list like this. It will take a while, since the original {\tt \textbackslash{}longtable} was more than nine pages long and full of table markup.

\subsection{The stage is set}\hypertarget{the-stage-is-set}{}\label{the-stage-is-set}

\begin{description}
\item[{\tt me}] well what have we here?

@@

\item[{\tt me}] hey look I can have a little dialog sortof

@@

\subsection{Progress and Stagnation}\hypertarget{progress-and-stagnation}{}\label{progress-and-stagnation}

\begin{description}
\item[{\tt me}] Keep going

\item[{\tt system}] OK!
\end{description}

\subsection{Innovation}\hypertarget{innovation}{}\label{innovation}

\begin{description}
\item[{\tt me}] Hey!

\item[{\tt system}] What?
\end{description}

\subsection{Frustrations}\hypertarget{frustrations}{}\label{frustrations}

(\&c)
